---
title: 'Week 2: Discussion'
author: "DSC 180A - Genetics"
date: "`r format(Sys.time(), '%Y/%m/%d')`"
output:
  html_document:
    theme: cosmo
    number_sections: yes
    toc: yes
    toc_float: true
    toc_depth: 3
---

All student responses are included for each question. Responses have been randomized within question. Questions with particularly strong responses are indicated with a leading **. (This does not mean the other responses were/are wrong or not good, just trying to highlight a few answers for each question to help students out.)

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

library(tidyverse)
library(knitr)
library(kableExtra)
library(googlesheets4)
options(gargle_oauth_email = "sellis@ucsd.edu")
```

```{r}
df <- read_sheet("1wKeS5_kYsCnFRt9SiRydX5meAqCpqvH0SsRJRi4-kyM") 

create_table <- function(x, n, seed){
  # randomize table order
  set.seed(seed)
  order <- sample(nrow(x))
  
  # generate output in randomm order
  x %>% 
  select(n) %>%
  arrange(order) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  scroll_box(width = "100%", height = "500px")
}
```

# `r colnames(df)[5]`

```{r}
create_table(df, 5, 1234)
```

# `r colnames(df)[6]`

```{r}
create_table(df, 6, 222)
```

# `r colnames(df)[7]`

```{r}
create_table(df, 7, 929)
```

# `r colnames(df)[8]`

```{r}
create_table(df, 8, 33)
```

# `r colnames(df)[9]`

```{r}
create_table(df, 9, 888)
```
